Spatial Reasoning and Statistical Graphics

### 2014-10-30 Paper/Draft1/TestingVisualAptitude.Rnw
tidying

<<partialregression, results='asis', echo=1>>=
model1 <- lm(lineup ~ vis_search, data=ans.summary)
print(xtable(summary(model1), caption="Results of the linear regression of visual search score on lineup score. \\label{vst-reg}."), sanitize.text.function=sanitize)
@
<<partialregression1,fig.keep='all', fig.width=4, fig.height=4, out.width='.45\\linewidth', fig.cap="Biplots of the adjusted lineup, card rotation, figure~classification, and paper folding scores principal components analysis. Adjusted lineup scores are most associated with figure~classification in the second principal component. In the third and fourth components, adjusted scores are almost entirely orthogonal. \\label{fig:biplot-adjusted}", tidy=T, echo=1:7>>=
# partial regression data set
ans.part <- ans.summary
ans.part$lineup <- resid(lm(lineup ~ vis_search, data=ans.summary))
ans.part$card_rot <- resid(lm(card_rot ~ vis_search, data=ans.summary))
ans.part$fig_class <- resid(lm(fig_class ~ vis_search, data=ans.summary))
ans.part$folding <- resid(lm(folding ~ vis_search, data=ans.summary))

@@

\item \textbf{Visual Argument Hypothesis}: Graphics require less processing because their visuospatial properties encode some of the information through the arrangement of elements as well as the elements themselves. That is, graphics are a form of ``external cognition"~\cite{scaife1996external} that guide, constrain, and facilitate cognitive behavior\cite{zhang1997nature}. This constraint reduces memory load and makes more cognitive resources available for other tasks; displays that clearly present information without deep processing requirements are more effective\cite{zhang1994representations}. Graphical displays have higher search and computational efficiency than text~\cite{larkin1987diagram}, and when graphics are designed according to gestalt principles of organization, where grouping lines up with visual chunks, gestalt heuristics can be used to more quickly encode information~\cite{shah1999graphs}.
\comment{\textit{I am working on making my way through all of this literature - right now, I'm re-citing stuff; I will print the papers out and add to this ASAP once I get toner into the printer.}}

>>>>

<<partialregression, results='asis', echo=1, tidy=T>>=
model1 <- lm(lineup ~ vis_search, data=ans.summary)
print(xtable(summary(model1), caption="Results of the linear regression of visual search score on lineup score. \\label{vst-reg}."), sanitize.text.function=sanitize)
@
<<partialregression1,fig.keep='all', fig.width=4, fig.height=4, out.width='.45\\linewidth', fig.cap="Biplots of the adjusted lineup, card rotation, figure~classification, and paper folding scores principal components analysis. Adjusted lineup scores are most associated with figure~classification in the second principal component. In the third and fourth components, adjusted scores are almost entirely orthogonal. \\label{fig:biplot-adjusted}", tidy=T, echo=1:7>>=
# partial regression data set
ans.part <- ans.summary
ans.part$lineup <- resid(lm(lineup ~ vis_search, data=ans.summary))
ans.part$card_rot <- resid(lm(card_rot ~ vis_search, data=ans.summary))
ans.part$fig_class <- resid(lm(fig_class ~ vis_search, data=ans.summary))
ans.part$folding <- resid(lm(folding ~ vis_search, data=ans.summary))

@@

\item \textbf{Visual Argument Hypothesis}: Graphics require less processing because their visuospatial properties encode some of the information through the arrangement of elements as well as the elements themselves. Displays that clearly present information without deep processing requirements are more effective\cite{zhang1994representations}. Graphical displays have higher search and computational efficiency than text~\cite{larkin1987diagram}, and when graphics are designed according to gestalt principles of organization, where grouping lines up with visual chunks, gestalt heuristics can be used to more quickly encode information~\cite{shah1999graphs}.
